Deep Variation Transformation for Foreground Detection

### 2019-03-08 draft.tex
.

As for the case of the shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
For traditional approaches, these shadow regions are usually segmented as foreground since they also movie with the objects. 
Therefore, traditional methods like PAWCS, WeSamBE and SharedModel falsely segment part of shadows as moving objects. 
In addition, the foreground provided by IUTIS-5 is incomplete on part of the pedestrian's body due to the interference of shades, 
because of the severe dependency on texture features. 
On the other hand, DeepBS performs well for this video benefiting from the utilization of CNN. 
However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
In contrast, since our DPVL focusses on learning the pattern of pixels' variation in the shadow regions, 
the proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.

>>>>

As for the case of the shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
For traditional approaches, these shadow regions are usually segmented as foreground since they also movie with the objects. 
Therefore, traditional methods like PAWCS, WeSamBE and SharedModel falsely segment part of shadows as moving objects. 
In addition, the foreground provided by IUTIS-5 is incomplete on part of the pedestrian's body due to the interference of shades, 
because of the severe dependency on texture features. 
On the other hand, DeepBS performs well for this video benefiting from the utilization of CNN. 
However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
In contrast, since our DPVTL focusses on learning the pattern of pixels' variation in the shadow regions, 
the proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.
